Verifying Demonstrations

### 2018-11-30 paper/protocol.tex
better notations in verification

To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

>>>>

To verify the participation count for a protest \(\prtst\) with identifier \(cid_0\),
a verifier must download from the storage system S the set \(S_{\prtst}\) of all \(s_P\) and \(s_W\) tuples containing \(cid_0\).
Then from \(S_{\prtst}\), a verifier can build, in succession,
(a) the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P,s_W)\) corresponding to a witness  \(i\) and a protester \(j\),
(b) the participation proof \(\prf_{j}\) for each protester \(j\),
(c) the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs for all protesters in \(P\),
 and finally the participation count, cardinality of the previous set.

More precisely, given: \\
\(S_{\prtst} = \{ (cid, pid, wid, l, t_s, t_s', t_c, \corr) \in \pshs \mid \cid = \cid_0 \} \) \\
and a matching pair \((s_P, s_W) \in {S_{\prtst}}^2\) for a witness \(i\) and a protester \(j\)
with \(s_P = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c, \psi_i)\)
and  \(s_W = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c', \psi_j)\),
%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
the verifier can build a valid proof share \(s_j^{(i)}\) certified by  \(i\) for \(j\) as follow:
verify \(\psi_i\) and \(\psi_j\),
let \(t = [max(t_s, t_s'), min(t_c, t_c')]\),
let \(s_j^{(i)} = (cid_0, pid_j, wid_i, l, t)\), as in \cref{DefProofShare},
check that \(s_j^{(i)}\) is valid (i.e. happened during and at the location of the protest), as in \cref{DefProofShare}.

Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst)\), as in \cref{DefParticipationProof}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationProof}.

% MOST PROBABLY obsolete below v

%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
%(see \cref{DefProtest}), a verifier must download all the proof shares \[
%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
%\(l_i\subseteq  l\).
%Any proof share that does not verify correctly will be discarded.
%At this point, the verifier has constructed the set \(S\) from 
%\cref{DefProofShares} and can thus construct any participation proof 
%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
%    \theta}|\) as in \cref{DefParticipationCount}.

%__________________________
